Our Beautiful Paper

### 2022-09-11 cpp/submission.tex
Added some prose in the introduction and background sections

\section{Introduction}
\label{sec:introduction}

@@

\subsection{Graphs and strongly connected components}
\label{sec:graphs}

@@

>>>>

\section{Introduction}
\label{sec:introduction}
Directed graphs are widely used in many fields of computer science and mathematics.
The study of their properties is therefore an important topic because of their application in areas that may affect our lives.

They are also heavily used in critical domains that indirectly affect us, such as model checking.
Indeed, as model checking involves exhaustive exploration of graphs of states, it is important to have efficient -- and correct -- algorithms to perform different operations such as the computation of strongly connected components.

@@

\subsection{Graphs and strongly connected components}
\label{sec:graphs}
Graphs referred to in this paper are finite directed graphs.
The proof relies on the notion of reachability in a graph, which is defined inductively through the notion of successor in a directed graph.

A strongly connected component (SCC) of such a graph is a subset of its set of vertices such that two vertices of it are symmetrically reachable from each other.
More specifically, if $\mathcal{V}$ is the set of vertices of a graph $\mathcal{G}$ and if $\Rightarrow^*$ denotes reachability as the reflexive and transitive closure of the \emph{successor} binary relation, then a subset $\mathcal{C}$ of $\mathcal{V}$ is a SCC if:
\begin{equation*}
  \forall u, v \in \mathcal{C} \quad u \Rightarrow^* v \wedge v \Rightarrow^* u
\end{equation*}
Informally, SCCs roughly denote -- or a a generalisation of -- cycles in a graph.

@@

Isabelle is a generic proof assistant \cite{nipkow_isabellehol_2002} allowing mathematical formulas to be expressed in a formal language.
It provides tools for proving those formulas in a logical calculus.
Isabelle proofs are written in the Isar (``Intelligible Semi-Automated Reasoning'') language that is designed to make proofs readable and comprehensible for a mathematically inclined reader, with minimal overhead introduced by the formalism.
